### 2016-01-20 articles/almost-compatible-functions-and-topological-games/article.tex
misc work on gamma functions notes and alcomp preprint

 \begin{lemma}[\cite{MR597342}]
    Assume that \(G\subset \operatorname{Fn}(\omega_2,2)\) is a generic filter,
    and let \(\mu\in \omega_2\). Then the final model \(V[G]\) can be
    regarded as forcing with
    \(\operatorname{Fn}(\omega_2\setminus \mu, 2)\) over the model \(V[G_\mu]\).
    Let \(\dot n,\ddot n\) be a
    \(\operatorname{Fn}(\omega_2,2)\)-,
    \(\operatorname{Fn}(\omega_2\setminus\mu,2)\)-name respectively for each
    \(n<\omega\). Then for each \(\operatorname{Fn}(\omega_2,2)\)-name \(\dot A\)
    for \(A\subseteq\omega\), there is a canonical
    \(\operatorname{Fn}(\omega_2\setminus \mu, 2)\)-name
    \[
      \ddot A
        =
      \{
        (\ddot n,p\rest [\mu,\omega_2))
      :
        (\dot n,p)\in \dot A
      \}
    \]
    which satisfies
    \(
      A
        =
      \operatorname{val}(\dot A,G)
        =
      \operatorname{val}(\ddot A,G_\mu)
    \).
  \end{lemma}

  \begin{theorem}
    It follows from the consistency of \(ZFC\) that
    there exists a model of \(ZFC\) for which \(\mf c=\aleph_2\)
    and \(\neg\alcompS{\aleph_2}\).
  \end{theorem}

  \begin{proof}
    The forcing poset is \(\mb P=\operatorname{Fn}(\omega_2, 2)\).
    Let \(\{ \dot f_{A} : A\in [\omega_2]^\omega\}\) be a family of
    \(\mb P\)-names such that \(f_{A}\) is a one-to-one function from \(A\) into
    \(\omega\) in the ground model. Let \(M\) be an elementary submodel
    of the universe containing \(\mb P\) such that
    \(|M|=\omega_1 =\mathfrak c\) and \(M^\omega\subset M\).

    Let \(\lambda\) be the ordinal \(M\cap \omega_2\).
    We may assume
    \(
      \dot f_{[\lambda,\lambda+\omega)}
        =
      \{
        ((\lambda+k_p,m_p)^\cdot, p)
      :
        p\in C
      \}
    \)
    for some countable \(C\subseteq\operatorname{Fn}(\omega_2,\omega)\).
    Let
    \(
      \operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})
        =
      \bigcup_{p\in C}\operatorname{dom} p
    \).

    Let \(\delta_\lambda\) denote the order type of
    \(\operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})\setminus \lambda\),
    and for \(\mu\leq\lambda\) let \(\varphi_{\mu,\lambda}'\) be the
    order-preserving bijection from
    \(
      \mu\cup
      \left(\operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})
        \setminus
      \lambda\right)
    \)
    onto the ordinal \(\mu+\delta_\lambda\).
    This lifts canonically to an order-preserving bijection
    \(
      \varphi_{\mu,\lambda}
        :
      \operatorname{Fn}(\mu\cup Y,2)
        \to
      \operatorname{Fn}(\mu+\delta,2)
    \).

    Consider the \(\mb P\)-name
    \(
      F_M
        =
      \{
        ((\lambda+k_p,m_p)^\cdot,\varphi_{\mu,\lambda}(p))
      :
        ((\lambda+k_p,m_p)^\cdot,p)\in\dot f_A
      \}
    \).

    % Other values
    %         replacing \(\lambda>\mu\) will result in their own set \(Y\)
    %         and canonical map \(\varphi_{\mu,\lambda}\); but one thing we do have to
    %         assume (or arrange) for other values \(\alpha\) replacing \(\lambda\)
    %         is that \(\operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})\)
    %         intersected with
    %         \(\alpha\) is contained in \(\mu\).

            Now the object \(F_M\) is an
            element of \(M\), and \(M\) believes this statement is true:
            \[
            (\forall \beta\in\omega_2)~ (\exists \beta<\lambda\in \omega_2)~~~
            \operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})
            \cap \lambda\subset \mu \ \ \mbox{and}\ \
            F_M = \varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})\]

            But now, this  means that,
            not only is there  an \(\alpha\in M\),
            \( F_M = \varphi_{\mu,\alpha}(\dot f_{[\alpha,\alpha+\omega)})\)
            but also that there is an increasing sequence
             \(\{\alpha_\xi : \xi  \in \omega_1\}\subset \lambda\) of
             such \(\alpha\)'s satisfying that, for each \(\xi\)
            we have that \(\operatorname{supp}(\dot
            f_{[\alpha_\xi,\alpha_\xi+\omega)})\) is contained in \(\alpha_{\xi+1}\).

            Choose such a sequence.
             This means that if we let \(A = \bigcup_{n>0} [\alpha_n,\alpha_n+\omega)\) we
             have the name \(\dot f_A\) in \(M\). This then means that all
             the \(( (\beta,m) , p)\) appearing in \(\dot f_A\) have the property
             that \(\mathop{dom}(p)\) is contained in \(M\).
            There is, within \(M\), a name \(\dot g\) satisfying that
             \(\dot f_A(\alpha_n+k) = \dot f_{[\alpha_n,\alpha_n+\omega)}(\alpha_n+k)\)
            for all \(k >\dot g(n)\).

            We now apply the above Lemma using \(\mu = \mu_0\) and we are now
            working in the extension \(V[G_\mu]\). We will abuse the notation
            and use \(\dot f_{[\alpha_n,\alpha_n+\omega)}\) instead of
              \(\dot f_{[\alpha_n,\alpha_n+\omega)}(G_{\mu})\) as defined in
              the Lemma.
            We work for a contradiction. Something special has now happened,
             namely,  the supports of the names \(\{
            \dot f_{[\alpha_n, \alpha_n+\omega)} :  0< n<\omega\}\) are pairwise disjoint
            and also disjoint from the support of the name
             \(\dot f_{[\lambda,\lambda+\omega)}\) (under the same convention about
             \(G_\mu\).  And not only that, these names are pairwise isomorphic (in
             the way that they all map to \(F_M\)).

@@

            Choose \(n\) large enough so that \(\mathop{dom}(q) \cap [\alpha_n,
            \mu_{n+1})\) is
            empty.
             Choose \(q_1<q\restriction \lambda\) (in \(M\)) so that
            \[ \varphi_{\mu,\alpha_n}(q_1\restriction \operatorname{supp}(
             \dot f_{[\alpha_n,\alpha_n+\omega)}) =
            \varphi_{\mu,\lambda}(q\restriction \operatorname{supp}(
             \dot f_{[\lambda,\lambda+\omega)}) \]
            and then (again in \(M\)) choose \(q_2 < q_1\)
            so that it both forces a value
             \(L\) on \(\ell+\dot g(n)\)
            and subsequently forces a value \(m\) on
             \(\dot f_{[\alpha_n, \alpha_n+\omega)}(\alpha_n+L+1)\).
            But now, again calculate
            \[ q_3 = \varphi_{\mu,\lambda}^{-1} \circ \varphi_{\mu,\alpha_n}
            (q_2\restriction \operatorname{supp}(\dot
            f_{[\alpha_n,\alpha_n+\omega)}))\]
            and, by the isomorphisms, we have that \(q_3\) forces that
             \(\dot f_{[\lambda,\lambda+\omega)}(\lambda+L+1) = m\).

@@

            Follow
            the bouncing ball: it suffices to consider
             \(q(\beta)=e\) and to assume that \(q_3(\beta)\) is defined.
            Since \(q_3(\beta)\) is defined, we have that
            there is a  \(\beta'\in\mathop{dom}(q_2)\) such that \(
             \varphi_{\mu,\lambda}(\beta) = \varphi_{\mu,\alpha_n}(\beta')\),
            and that \(q_3(\beta) = q_2(\beta')\).
            But, by definition of \(q_1\), \(\beta'\in\mathop{dom}(q_1)\)
            and even  that \(q_1(\beta') = q(\beta)\).
             Then, since \(q_2<q_1\), we have that \(q_2(\beta')=q_1(\beta') =
             q(\beta)\). This completes the circle that \(q_3(\beta) = q(\beta)\).
            \bigskip

>>>>

 \begin{lemma}[\cite{MR597342}]
    Assume that \(G\subset \operatorname{Fn}(\omega_2,2)\) is a generic filter
    over a model \(M\),
    and let \(\mu\in \omega_2\). Then the generic extension \(M[G]\) can be
    regarded as forcing with
    \(\operatorname{Fn}(\omega_2\setminus \mu, 2)\) over the model \(M[G_\mu]\).
    Let \(\dot n,\ddot n\) be a
    \(\operatorname{Fn}(\omega_2,2)\)-,
    \(\operatorname{Fn}(\omega_2\setminus\mu,2)\)-name respectively for each
    \(n<\omega\). Then for each \(\operatorname{Fn}(\omega_2,2)\)-name \(\dot A\)
    for \(A\subseteq\omega\), there is a canonical
    \(\operatorname{Fn}(\omega_2\setminus \mu, 2)\)-name
    \[
      \ddot A
        =
      \{
        (\ddot n,p\rest [\mu,\omega_2))
      :
        (\dot n,p)\in \dot A
      \}
    \]
    which satisfies
    \(
      A
        =
      \operatorname{val}(\dot A,G)
        =
      \operatorname{val}(\ddot A,G_\mu)
    \).
  \end{lemma}

  \begin{theorem}
    There exists a model of \(ZFC\) for which \(\mf c=\aleph_2\)
    and \(\neg\alcompS{\aleph_2}\).
  \end{theorem}

  \begin{proof}
    The forcing poset is \(\mb P=\operatorname{Fn}(\omega_2, 2)\).
    Let \(\{ \dot f_{A} : A\in [\omega_2]^\omega\}\) be a family of
    \(\mb P\)-names such that \(f_{A}\) is a one-to-one function from \(A\)
    into \(\omega\) in the ground model. Let \(M\) be an elementary submodel
    of \(ZFC+CH\) containing all its countable subsets, containing \(\mb P\),
    and satisfying \(|M|=\omega_1 =\mathfrak c\).

    Let \(\lambda\) be the ordinal \(M\cap \omega_2\). For
    \(\alpha\leq\lambda\) we may assume
    \(
      \dot f_{[\alpha,\alpha+\omega)}
        =
      \{
        ((\alpha+k_p,m_p)^\cdot, p)
      :
        p\in C_\alpha
      \}
    \)
    for some countable \(C_\alpha\subseteq\operatorname{Fn}(\omega_2,\omega)\).
    Let
    \(
      \operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})
        =
      \bigcup_{p\in C_\alpha}\operatorname{dom} p
    \).

    For each \(\alpha\leq\lambda\),
    let \(\delta_{\alpha}\) denote the order type of
    \(\operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})\setminus \alpha\),
    and when \(\mu\leq\alpha\) and
    \(
      \operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})
        \cap
      \alpha
        \subseteq
      \mu
    \)
    let \(\varphi'_{\mu,\alpha}\) be the order-preserving bijection from
    \(
      \mu\cup
      \left(\operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})
        \setminus
      \alpha\right)
    \)
    onto the ordinal \(\mu+\delta_\alpha\).
    This lifts canonically to an order-preserving bijection
    \(
      \varphi_{\mu,\alpha}
        :
      \operatorname{Fn}(\mu\cup
        \left(\operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})
          \setminus
        \alpha\right)
      ,2)
        \to
      \operatorname{Fn}(\mu+\delta_\alpha,2)
    \).

    We now fix \(\mu<\lambda\) such that
    \[
      \bigcup_{\alpha\leq\lambda}
      \operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})
        \cap
      \alpha
        \subseteq
      \mu
    \]
    (TODO how?) and define the \(\mb P\)-name
    \[
      F
      %   =
      % \varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})
        =
      \{
        ((\lambda+k_p,m_p)^\cdot,\varphi_{\mu,\lambda}(p))
      :
        ((\lambda+k_p,m_p)^\cdot,p)\in\dot f_{[\lambda,\lambda+\omega)}
      \}
    .\]

    So in \(M\), we may reason (TODO why)
    that for each \(\beta<\omega_2\) there exists
    some \(\alpha\in\omega_2\setminus\beta\) where
    \[
      \operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})
      \cap \alpha\subseteq \mu
    \]
    and
    \[
      F
        =
      \{
        ((\alpha+k_p,m_p)^\cdot,\varphi_{\mu,\alpha}(p))
      :
        ((\alpha+k_p,m_p)^\cdot,p)\in\dot f_{[\alpha,\alpha+\omega)}
      \}
    .\]

    But now, this means not only is there an \(\alpha<\lambda\) such that
    \( F = \varphi(\dot f_{[\alpha,\alpha+\omega)})\),
    but also that there is an increasing sequence
    \(\{\alpha_\xi : \xi  \in \omega_1\}\subseteq \lambda\)
    satisfying that \(F=\varphi(\dot f_{[\alpha_\xi,\alpha_\xi+\omega)})\) and
    \(\operatorname{supp}(\dot f_{[\alpha_\xi,\alpha_\xi+\omega)})\) is
    contained in \(\alpha_{\xi+1}\) (TODO why not \(\mu\)?).

    Choose such a sequence, and let
    \(A = \bigcup_{0<n<\omega} [\alpha_n,\alpha_n+\omega)\). Consider
    the name \(\dot f_A\) in \(M\). Note all the \(((\beta,m)^\cdot, p)\)
    appearing in \(\dot f_A\) have the property that
    \(\operatorname{dom}(p)\) is contained in \(M\) (QUESTION: isn't the
    domain of any member of \(\mb P\) in the domain?)
    There is, within \(M\), a name \(\dot g\) satisfying that
     \(\dot f_A(\alpha_n+k) = \dot f_{[\alpha_n,\alpha_n+\omega)}(\alpha_n+k)\)
    for all \(k >\dot g(n)\) (TODO: why?).

    (TODO catch up to here)

            We now apply the above Lemma and work in \(M[G_\mu]\).
            We work for a contradiction. Something special has now happened,
            namely,  the supports of the names \(\{
            \dot f_{[\alpha_n, \alpha_n+\omega)} :  0< n<\omega\}\) are pairwise disjoint
            and also disjoint from the support of the name
            \(\dot f_{[\lambda,\lambda+\omega)}\) (under the same convention about
            \(G_\mu\).  And not only that, these names are pairwise isomorphic (in
            the way that they all map to \(F_M\)).

@@

            Choose \(n\) large enough so that \(\mathop{dom}(q) \cap [\alpha_n,
            \mu_{n+1})\) is
            empty.
             Choose \(q_1<q\restriction \lambda\) (in \(M\)) so that
            \[ \varphi_{\mu,\alpha_n}(q_1\restriction \operatorname{supp}(
             \dot f_{[\alpha_n,\alpha_n+\omega)}) =
            \varphi(q\restriction \operatorname{supp}(
             \dot f_{[\lambda,\lambda+\omega)}) \]
            and then (again in \(M\)) choose \(q_2 < q_1\)
            so that it both forces a value
             \(L\) on \(\ell+\dot g(n)\)
            and subsequently forces a value \(m\) on
             \(\dot f_{[\alpha_n, \alpha_n+\omega)}(\alpha_n+L+1)\).
            But now, again calculate
            \[ q_3 = \varphi^{-1} \circ \varphi_{\mu,\alpha_n}
            (q_2\restriction \operatorname{supp}(\dot
            f_{[\alpha_n,\alpha_n+\omega)}))\]
            and, by the isomorphisms, we have that \(q_3\) forces that
             \(\dot f_{[\lambda,\lambda+\omega)}(\lambda+L+1) = m\).

@@

            Follow
            the bouncing ball: it suffices to consider
             \(q(\beta)=e\) and to assume that \(q_3(\beta)\) is defined.
            Since \(q_3(\beta)\) is defined, we have that
            there is a  \(\beta'\in\mathop{dom}(q_2)\) such that \(
             \varphi(\beta) = \varphi_{\mu,\alpha_n}(\beta')\),
            and that \(q_3(\beta) = q_2(\beta')\).
            But, by definition of \(q_1\), \(\beta'\in\mathop{dom}(q_1)\)
            and even  that \(q_1(\beta') = q(\beta)\).
             Then, since \(q_2<q_1\), we have that \(q_2(\beta')=q_1(\beta') =
             q(\beta)\). This completes the circle that \(q_3(\beta) = q(\beta)\).
            \bigskip

### 2016-01-20 postdoctoral/gamma_functions.tex
misc work on gamma functions notes and alcomp preprint

  \begin{definition}
    Let a V-map be a u.s.c. idempotent surjection.
  \end{definition}

@@

  \begin{theorem}
    Every V-map on a compact connected LOTS satisfies condition \(\Gamma\).
  \end{theorem}

  This was proven in \cite{CLONTZVARAGONA} for the case \(M\) is a closed
  interval of real numbers; however, the same proof applies to this more
  general case.

@@

  \begin{definition}
    For any LOS \(\<L,\leq\>\), let \(\check L\) be the collection of
    leftward subsets of \(L\)
    (subsets for which \(b\in L,a\leq b\Rightarrow a\in L\))
    linearly ordered by \(\subseteq\), and let \(\hat L\) be the collection
    of left-closed subsets of \(L\) (leftward subsets which are closed)
    linearly ordered by \(\subseteq\).
  \end{definition}

  \begin{proposition}
    \(\check L\), \(\hat L\) are compact.
  \end{proposition}

@@

    If \(L\) is countable, then note that the union of
    \(\mc S=\{((\leftarrow,l),L]:l\in L\}\) and
    \(\mc T=\{[\emptyset,(\leftarrow,l]):l\in L\}\)
    generates a countable base for \(\check L\).
  \end{proof}

@@

  \begin{example}
    For limit ordinals \(\alpha\), \(\hat \alpha\cong \alpha+1\),
    and for all other infinite ordinals, \(\hat\alpha\cong\alpha\).
    (The addition of a new least isolated point is of course irrelevant).
  \end{example}

@@

  \begin{proof}
    Since \(\check\alpha=\alpha+1\) (actually equals, not just homeomorphic!),
    we get \(\varprojlim^\star \{2, \gamma, \alpha\}
      \cong \check\alpha =
    \alpha+1\) for free.
    Note that C and Varagona used this in (TODO create citataion) to break
    metrizability in uncountable-ordinal-indexed inverse limits (for any V-map
    there exists a two-point set \(2\) such that \(f\rest 2\supseteq\gamma\),
    that is, ``\(f\) has condition \(\Gamma\)'').
  \end{proof}

@@

  We may generalize theorem whatevs as follows:

  \begin{theorem} %TODO fix first \sim to use A,B instead of l_0,l_1
    If \(M\) is a LOTS with minimum \(0\) and maximum \(1\),
    then \(\varprojlim\{M,\gamma,L\}\cong \hat L\lexTimes M/\sim\),
    where \(\<(\leftarrow,l_0],1\>\sim\<(\leftarrow,l_1],0\>\) if
    \(l_0<l_1\) and \((l_0,l_1)=\emptyset\),
    and where \(\<A,m\>\sim\<A,m'\>\) if \(A\in\hat L\setminus L\).
  \end{theorem}

@@

    A basic open set in \(\varprojlim\{M,\gamma,L\}\subseteq L^m\)
    is of the form
    \(\lb U,F \rb\) where \(U(l)\) is an open interval in \(M\) for each
    \(l\in F\in [L]^{<\omega}\), and
    \(\lb U,F\rb=\{\vect x:l\in F\Rightarrow\vect x(l)\in U(l)\}\).
    If we assume that \(\lb U,F \rb\) is non-empty, one of the following
    must hold:

@@

  We now discard the linear order on \(M\). Denote points in the topological
  sum \(\bigoplus_{l\in \hat L} M\) of \(\hat L\) copies of \(M\)
  by the ordered pairs \(\<A,m\>\)
  for \(A\in \hat L\), \(m\in M\). The previous proof may be generalized to
  show the following:

  \begin{theorem}
    If \(M\) is a Hausdorff space with points \(0\) and \(1\),
    then \(\varprojlim\{M,\gamma,L\}\cong \bigoplus_{l\in \hat L} M/\sim\),
    where \(\<(\leftarrow,l_0],1\>\sim\<(\leftarrow,l_1],0\>\) if
    \(l_0<l_1\) and \((l_0,l_1)=\emptyset\),
    and where \(\<A,m\>\sim\<A,m'\>\) if \(A\in\hat L\setminus L\).
  \end{theorem}

>>>>

  All spaces are assumed to be Hausdorff. Continuum means ``Hausdorff, compact,
  and connected''.

  \begin{definition}
    A generalized inverse limit \(\varprojlim \{X_p, f_{p,q}, D\}\) is a
    subspace of \(\prod_{p\in D}X_p\) defined for
    a directed set \(\<D,\leq\>\),
    topological spaces \(X_p\) for each \(p\in D\),
    and relations \(f_{p,q}\subseteq X_q\times X_p\) for each
    \(p,q\in D\) where \(p\leq q\). Elements in  \(\varprojlim \{X, f, D\}\)
    are the sequences \(\vect x\) such that \(p\leq q\) implies
    \(\vect x(p)\in f_{p,q}(\vect x(q))\).
  \end{definition}

  \begin{definition}
    An uppersemicontinuous (u.s.c.) relation is a closed subset of the
    square.
  \end{definition}

  \begin{theorem}[summarized in \cite{VARAGONApreprint}]
    If \(L\) is totally ordered, \(X_p\) is a continuum for all \(p\in L\),
    and \(f_{p,q}\) is u.s.c. and continuum-valued for each \(p\leq q\in L\),
    then \(\varprojlim\{X,f,L\}\) is a continuum.
  \end{theorem}

  \begin{definition}
    An idempotent relation on \(X^2\) satisfies \(f[f(x)]=f(x)\) for all
    \(x\in X\).
  \end{definition}

  \begin{definition}
    A V-map \(f\subseteq X^2\) is a continuum-valued u.s.c. idempotent
    surjection.
  \end{definition}

@@

  \begin{theorem}[\cite{CLONTZVARAGONA}]
    Every V-map on a compact connected LOTS satisfies condition \(\Gamma\).
  \end{theorem}

@@

  Assume \(L\) is a total order.

  \begin{definition}
    For any total order \(\<L,\leq\>\), let \(\check L\) be the collection of
    leftward subsets of \(L\)
    (subsets for which \(b\in L,a\leq b\Rightarrow a\in L\))
    linearly ordered by \(\subseteq\), and let \(\hat L\) be the collection
    of left-closed subsets of \(L\) (leftward subsets which are closed)
    linearly ordered by \(\subseteq\).
  \end{definition}

  \begin{proposition}
    \(\check L\), \(\hat L\) are compact LOTS.
  \end{proposition}

@@

    If \(L\) is countable, then note that the union of
    \(\mc S=\{((\leftarrow,l),L]:l\in L\}\) and
    \(\mc T=\{[\emptyset,(\leftarrow,l]):l\in L\}\)
    is a countable subbase for \(\check L\).
  \end{proof}

@@

  \begin{example}
    For finite and limit ordinals \(\alpha\), \(\hat \alpha\cong \alpha+1\),
    and for all other ordinals, \(\hat\alpha\cong\alpha\).
  \end{example}

@@

  \begin{proof}
    Since \(\check\alpha=\alpha+1\) (actually equals, not just homeomorphic!),
    we get \(\varprojlim \{2, \gamma, \alpha\}
      \cong \check\alpha =
    \alpha+1\) for free.
    This is essentially what the author and Varagona used
    in \cite{CLONTZVARAGONA} to break
    metrizability in uncountable-ordinal-indexed inverse limits.
  \end{proof}

@@

  We may generalize theorem 15 as follows:

  \begin{theorem}
    If \(M\) is a LOTS with minimum \(0\) and maximum \(1\),
    then \(\varprojlim\{M,\gamma,L\}\cong \hat L\lexTimes M/\sim\),
    where \(\<A,1\>\sim\<B,0\>\) if
    \(A\subsetneq B\) and \((A,B)=\emptyset\),
    and where \(\<A,m\>\sim\<A,m'\>\) if \(A\in\hat L\setminus L\).
  \end{theorem}

@@

    A basic open set in \(\varprojlim\{M,\gamma,L\}\subseteq L^M\)
    is of the form
    \(\lb U,F \rb\) where \(U(l)\) is an open interval in \(M\) for each
    \(l\in F\in [L]^{<\omega}\), and
    \(\lb U,F\rb=\{\vect x:l\in F\Rightarrow\vect x(l)\in U(l)\}\).
    If we assume that \(\lb U,F \rb\) is non-empty, one of the following
    must hold:

@@

  % We now discard the linear order on \(M\). Denote points in the topological
  % sum \(\bigoplus_{l\in \hat L} M\) of \(\hat L\) copies of \(M\)
  % by the ordered pairs \(\<A,m\>\)
  % for \(A\in \hat L\), \(m\in M\). The previous proof may be generalized to
  % show the following:

  % \begin{theorem}
  %   If \(M\) is a Hausdorff space with points \(0\) and \(1\),
  %   then \(\varprojlim\{M,\gamma,L\}\cong \bigoplus_{l\in \hat L} M/\sim\),
  %   where \(\<(\leftarrow,l_0],1\>\sim\<(\leftarrow,l_1],0\>\) if
  %   \(l_0<l_1\) and \((l_0,l_1)=\emptyset\),
  %   and where \(\<A,m\>\sim\<A,m'\>\) if \(A\in\hat L\setminus L\).
  % \end{theorem}
